User Preferences in Graphical and Textual Interfaces for Kubernetes

### 2021-08-24 Draft.tex
added formatting for tables
reformat tables

\documentclass[11pt, oneside]{article}   	% use "amsart" instead of "article" for AMSLaTeX format
\usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   		% ... or a4paper or a5paper or ... 
%\geometry{landscape}                		% Activate for rotated page geometry
%\usepackage[parfill]{parskip}    		% Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}				% Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
								% TeX will automatically convert eps --> pdf in pdflatex	
\usepackage{array}
\usepackage{amssymb}
\usepackage{todonotes}
\usepackage{caption}

@@

\subsection{Interpretation}
\subsubsection{Exhaustion}
We collected the user input frequencies as a measure of exhaustion due to the total number of interactions required to complete the task. These frequencies are shown for each participant in Tables 1-4.
\subsubsection{Disruption}
We kept track of the specific commands participants used, the inputs that make up those commands, and patterns of switching between different inputs (composed as regular expressions) as a measure of disruption due to the number of times the participant had to task switch (for example, between typing and mousing) to complete the task.

@@

\begin{table}
 \centering
  \begin{tabular}{ | c | c | c | c | c | }
  \hline
  P1 & Copy/Paste & Keyboard & Click & Page Navigation \\ 
  \hline
  kubectl CLI & 6 & 15 & 8 & 22 \\ 
  \hline
  OpenShift console & 0 & 2 & 77 & 80 \\ 
  \hline
  \end{tabular}
 \caption{P1 input frequencies}
\end{table}

\begin{table}
 \centering
  \begin{tabular}{ | c | c | c | c | c | } 
  \hline
  P2 & Copy/Paste & Keyboard & Click & Page Navigation \\ 
  \hline
  kubectl CLI & 7 & 28 & 20 & 49 \\ 
  \hline
  OpenShift console & 0 & 13 & 145 & 172 \\ 
  \hline
  \end{tabular}
 \caption{P2 input frequencies}
\end{table}

\begin{table}
 \centering
  \begin{tabular}{ | c | c | c | c | c | } 
  \hline
  P3 & Copy/Paste & Keyboard & Click & Page Navigation \\ 
  \hline
  kubectl CLI & 1 & 17 & 1 & 3 \\ 
  \hline
  OpenShift console & 4 & 5 & 142 & 192 \\ 
  \hline
  \end{tabular}
 \caption{P3 input frequencies}
\end{table}

\begin{table}
 \centering
  \begin{tabular}{ | c | c | c | c | c | } 
  \hline
  P4 & Copy/Paste & Keyboard & Click & Page Navigation \\ 
  \hline
  kubectl CLI & 0 & 32 & 2 & 1 \\ 
  \hline
  OpenShift console & 4 & 14 & 133 & 137 \\ 
  \hline
  \end{tabular}
 \caption{P4 input frequencies}
\end{table}

\begin{center}
\begin{tabular}{ | c | c | c | } 
  \hline
  P1 & kubectl CLI & OpenShift console \\ 
  \hline
   &  &  \\ 
  \hline
\end{tabular}
\end{center}

\begin{center}
\begin{tabular}{ | c | c | c | } 
  \hline
  P2 & kubectl CLI & OpenShift console \\ 
  \hline
   &  &  \\ 
  \hline
\end{tabular}
\end{center}

\begin{center}
\begin{tabular}{ | c | c | c | } 
  \hline
  P3 & kubectl CLI & OpenShift console \\ 
  \hline
   &  &  \\ 
  \hline
\end{tabular}
\end{center}

\begin{center}
\begin{tabular}{ | c | c | c | } 
  \hline
  P4 & kubectl CLI & OpenShift console \\ 
  \hline
   &  &  \\ 
  \hline
\end{tabular}
\end{center}

>>>>

\documentclass[11pt, oneside]{article}   	% use "amsart" instead of "article" for AMSLaTeX format
\usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   		% ... or a4paper or a5paper or ... 
%\geometry{landscape}                		% Activate for rotated page geometry
%\usepackage[parfill]{parskip}    		% Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}				% Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
								% TeX will automatically convert eps --> pdf in pdflatex	
\usepackage{array}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{todonotes}
\usepackage{caption}

@@

\subsection{Interpretation}
\subsubsection{Exhaustion}
We collected the user input frequencies as a measure of exhaustion due to the total number of interactions required to complete the task. These frequencies are shown for each participant in Tables \text{\ref{table:t1}--\ref{table:t4}}.
\subsubsection{Disruption}
We kept track of the specific commands participants used, the inputs that make up those commands, and patterns of switching between different inputs (composed as regular expressions) as a measure of disruption due to the number of times the participant had to task switch (for example, between typing and mousing) to complete the task.

@@

\begin{table}
 \centering
  \begin{tabular}{ | c | c | c | c | c | }
  \hline
  P1 & Clicks & Commands & Mouse Movements \\ 
  \hline
  kubectl CLI & 8 & 21 & 22 \\ 
  \hline
  OpenShift Console & 77 & 2 & 80 \\ 
  \hline
  \end{tabular}
 \caption{P1 input frequencies.}
 \label{table:t1}
\end{table}

\begin{table}
 \centering
  \begin{tabular}{ | c | c | c | c | c | } 
  \hline
  P2 & Clicks & Commands & Mouse Movements \\ 
  \hline
  kubectl CLI & 20 & 35 & 49 \\ 
  \hline
  OpenShift Console & 145 & 13 & 172 \\ 
  \hline
  \end{tabular}
 \caption{P2 input frequencies.}
 \label{table:t2}
\end{table}

\begin{table}
 \centering
  \begin{tabular}{ | c | c | c | c | c | } 
  \hline
  P3 & Clicks & Commands & Mouse Movements \\ 
  \hline
  kubectl CLI & 1 & 18 & 3 \\ 
  \hline
  OpenShift Console & 142 & 9 & 192 \\ 
  \hline
  \end{tabular}
 \caption{P3 input frequencies.}
 \label{table:t3}
\end{table}

\begin{table}
 \centering
  \begin{tabular}{ | c | c | c | c | c | } 
  \hline
  P4 & Clicks & Commands & Mouse Movements \\ 
  \hline
  kubectl CLI & 2 & 32 & 1 \\ 
  \hline
  OpenShift Console & 133 & 18 & 137 \\ 
  \hline
  \end{tabular}
 \caption{P4 input frequencies.}
 \label{table:t4}
\end{table}

\begin{table}
 \centering
  \begin{tabular}{ | c | c | c | c | c | } 
  \hline
  Total & Clicks & Commands & Mouse Movements \\ 
  \hline
  kubectl CLI & 31 & 106 & 75 \\ 
  \hline
  OpenShift Console & 497 & 42 & 581 \\ 
  \hline
  \end{tabular}
 \caption{Total input frequencies.}
 \label{table:t5}
\end{table}

\begin{table}
 \centering
  \begin{tabular}{ | c | c | c | } 
  \hline
  P1 & kubectl CLI & OpenShift Console \\ 
  \hline
  Command Execution &  &  \\ 
  \hline
  Copy/Paste & & \\
  \hline
  Navigation & & \\
  \hline
  Tab Completion & & \\
  \hline
  \end{tabular}
 \caption{P1 regular expression patterns.}
\end{table}

\begin{table}
 \centering
  \begin{tabular}{ | c | c | c | } 
  \hline
  P2 & kubectl CLI & OpenShift Console \\ 
  \hline
  Command Execution &  &  \\ 
  \hline
  Copy/Paste & & \\
  \hline
  Navigation & & \\
  \hline
  Tab Completion & & \\
  \hline
  \end{tabular}
 \caption{P2 regular expression patterns.}
\end{table}

\begin{table}
 \centering
  \begin{tabular}{ | c | c | c | } 
  \hline
  P3 & kubectl CLI & OpenShift Console \\ 
  \hline
  Command Execution &  &  \\ 
  \hline
  Copy/Paste & & \\
  \hline
  Navigation & & \\
  \hline
  Tab Completion & & \\
  \hline
  \end{tabular}
 \caption{P3 regular expression patterns.}
\end{table}

\begin{table}
 \centering
  \begin{tabular}{ | c | c | c | } 
  \hline
  P4 & kubectl CLI & OpenShift Console \\ 
  \hline
  Command Execution &  &  \\ 
  \hline
  Copy/Paste & & \\
  \hline
  Navigation & & \\
  \hline
  Tab Completion & & \\
  \hline
  \end{tabular}
 \caption{P4 regular expression patterns.}
\end{table}
